The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Adding OECD image
Image try
Added image from OECD publication

Chart about factors that affect entrepreneurship.
Source: OECD Local Entrepreneurship Reviews
Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.

@@

### Necessary Concepts  
1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.

@@

>>>>

Chart about factors that affect entrepreneurship.
Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.

@@

### Necessary Concepts

1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.

@@

<br>
<p align="center">
[<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
Source: OECD Local Entrepreneurship Reviews [@OECD2009]
</p>
